The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-19 draft/ms.tex
abstract update 2

The Exoplanet Orbit Database (EOD) collects orbital and stellar
parameters of all known exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available at exoplanets.org. We have
ZZZ number of confirmed exoplanets as of March 2014.  
Since \cite{Wright2011}, we made an effort to put robustly detected
exoplanets together with over 3000 sample of exoplanet candidates
(\kepler\ Objects of Interest, KOIs) and other planets (the ones
detected by microlensing, imaging, timing) on exoplanets.org. We also
added some new fields (e.g. the secondary eclipse depths), removed
obsolete fields, and revised some fields as necessary.

>>>>

The Exoplanet Orbit Database (EOD) collects orbital and stellar
parameters of all known robustly dected exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available at exoplanets.org. We have
ZZZ number of confirmed exoplanets as of March 2014.  
The first complete documentation for the EOD and the EDE was \cite{Wright2011} and since then, we have expanded the scope of the EOD and incorporated the sample of over 3000  \kepler\ Objects of Interest, (KOIs) and other planets (the ones detected by microlensing, imaging, and timing) on exoplanets.org. We also added some new fields (e.g. the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.
